\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
This document contains the work that I have been doing for the past eight months. These months just flew by and I enjoyed working on this multi-disciplinary project. Firstly, I am thankful to the almighty for providing me the strength to overcome various challenges I faced over the past two years of my master program which has been highly demanding. I have a long list of people whom I would like to thank and without whose support this project could not have been completed.
I would like to first thank my parents for providing me the financial support for coming to the Netherlands and doing my master studies at TU Delft. Without their encouragement and support, I would not be where I am now. Next, I would like to thank my master program coordinator and my supervisor, Arjan van Genderen who accepted to supervise me in this multi-disciplinary project. His invaluable guidance has been extremely helpful in this project and throughout my master program. 
I would like to thank Delfi Space Program Manager, Jasper Bouwmeester, who first introduced me to my second supervisor Hans Kuiper. Hans provided me the support and was instrumental in understanding the requirements for designing the imager. Next, I would like to thank Paul Urbach who introduced me to the Optica Research Group which is where I did all the experiments. I am extremely thankful to Ph.D. students, Yifeng Shao and Sander Konijnenberg. Yifeng was also my daily supervisor and helped me with understanding the theoretical physics, simulation of imaging algorithms and also on how to work with optical instruments. He continuously encouraged me to overcome challenges I faced along the way. I could not have asked for a better supervisor. I would also like to thank Sander for many discussions that very highly insightful and helped me to cross hurdles that I faced. On the whole, the Optica Research Group was a very nice place to work with very sociable people. I would like to thank the chair of the thesis committee, Stephan Wong for agreeing to be a part of the thesis committee. Lastly, I would like to thank my friends in Delft for their support and encouraging words in stressful times. \\


\noindent
Delft, The Netherlands

\noindent
\today
